---
  title: "Theoretical example calculations"
author: "Caitie"
date: "9/19/2019"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(NLMR)
library(landscapetools)
library(dplyr)
library(reshape2)
library(ggplot2)
library(fitdistrplus)
library(logspline)
library(MASS)
library(raster)
library(here)
library(purrr)
library(ggplot2)
library(broom)
devtools::install_github("johannesbjork/LaCroixColoR")
library(LaCroixColoR)
library(gridExtra)
library(tidyr)
library(data.table)
library(readr)

```


# Load pressure data

```{r}
source(here("scripts",'theme_nlm_nis.R'))

# Simplified version of the Poore data modified to be per kg liveweight


df2<-read_csv(here("data", "Poore_Nemecek_All_Stressors_revised.csv"), na = "-") %>% 
  filter(!is.na(value) == T) %>% 
  mutate(`LUC Burn` = replace_na(`LUC Burn`, 0),
         `LUC C Stock` = replace_na(`LUC C Stock`, 0),
         value = Farm + `LUC C Stock` + `LUC Burn`) %>% 
  dplyr::select(Product, stressor, value) %>% 
  rename(Category = Product) %>% 
  mutate(Category = ifelse(Category == "Maize", "Maize (Meal)",
                           ifelse(Category == "Beef", "Bovine Meat (Beef Herd)", "Fish (farmed)")),
         stressor = ifelse(stressor == "Freshwatr Withdr", "Freshwtr_Withdr", 
                    ifelse(stressor == "GHG_emissions", "GHG_emission",as.character(stressor))))
  
  
stressors <- unique(df2$stressor)
prod_types<-c("Maize (Meal)", "Bovine Meat (Beef Herd)", "Fish (farmed)")


# There is no wild fisheries here
# The new dataset does not have scientific name so we just use all salmon

sub_df<-df2 %>% 
  filter((Category %in% prod_types))

```


# Fisheries data

This data is from Hilborn et al. 2018 The environmental cost of animal source foods

"In all cases we calculated impacts for a standardized serving of 40 g of protein."

A herring edible/filet has 18% protein. So we can assume 1 kg herring = 0.18 kg protein or 180 g protein

https://esajournals.onlinelibrary.wiley.com/action/downloadSupplement?doi=10.1002%2Ffee.1822&file=fee1822-sup-0013-WebTableS3.pdf

```{r}

fish_df<-fread(here("data/Hilborn_LCA_data.csv")) %>% 
  filter(Category == "Fish",
         Wildorfarmed == "Wild",
         Product == "Smallpelagic") %>% 
  dplyr::select(Product, GHG_kg_CO2_eq_mean) %>% 
  rename(Category = Product, ghg_40g_protein = GHG_kg_CO2_eq_mean) %>% 
  mutate(stressor = "GHG_emission",
         ghg_40g_protein = as.numeric(ghg_40g_protein)) %>% 
  dplyr::select(Category, stressor, ghg_40g_protein) %>% 
  mutate(protein_conv_g = 180,
         ghg_g_protein = ghg_40g_protein/40) %>% 
  rename(value = ghg_g_protein) %>% 
  dplyr::select(Category,stressor,value)
```


# Join data together

```{r}
sub_df<-rbind(sub_df, fish_df)
```


## Investigate distribution of stressors 

```{r}
sub_df %>% 
  ggplot(aes(value)) + 
  geom_histogram() + 
  facet_grid(Category ~ stressor, scales = "free")

```

We use land use, ghg emissions and freshwater withdrawal to demonstrate our approach


```{r}

# As of now I do not remove the highest value
# I also remove all NAs whereas Nis changed NAs to 0

df_new <- sub_df %>% 
  filter(!is.na(value) == T) %>% 
  filter(!stressor %in% c("Water", "Acid_Pot", "Eutr")) %>% 
  mutate(value = value + 0.00001) %>% 
  group_by(Category, stressor) %>% 
  summarise(vec = value %>% list) %>% 
  mutate(mod = map(vec, ~fitdistrplus::fitdist(.x,'lnorm'))) %>% 
  mutate(meanlog = map(mod, ("estimate")) %>% map_dbl("meanlog")) %>% 
  mutate(sdlog = map(mod, ("estimate")) %>% map_dbl("sdlog"))

```


## Plot a simulated map of corn data
```{r}
set.seed(1234) # For reproducibility
fbm2 <- NLMR::nlm_fbm(100, 100, fract_dim = 1.1, resolution = 200) # Fractal dimension changes the landscape

plot(fbm2)

x <- util_classify(fbm2, weighting = c(0.1, 0.1, 0.3, 0.3, 0.03, 0.1), level_names = c("Corn","Beef", "Forest", "Water","Salmon aquaculture", "Small pelagic fishery"))
plot(x)

ratio <- nrow(x) / ncol(x)
legend_labels <-  x@data@attributes[[1]][, 2]

xyz  <- raster::as.data.frame(x, xy = TRUE)

p1 <-  ggplot(xyz) +
  geom_tile(aes(x, y, fill = factor(xyz[, 3]))) + theme_bw()+
  theme_nlm_nis(legend_labels = legend_labels, ratio = ratio)+
  scale_fill_manual(values = c('darkred','yellow', "darkgreen","darkorange",'lightblue', "darkblue"))+ 
  guides(fill=guide_legend(title="Landscape"))
p1    

```

# Determine stressor values for each cell in each food production category
```{r}
nrow_xyz<-table(xyz$layer_Categories) %>% 
  as.data.frame(row.names = NULL) %>% 
  mutate(Var1 = ifelse(Var1 == "Beef", "Bovine Meat (Beef Herd)", 
                       ifelse(Var1 == "Salmon aquaculture", "Fish (farmed)", 
                              ifelse(Var1 == "Corn","Maize (Meal)",
                                     ifelse(Var1 == "Forest", "Forest", 
                                            ifelse( Var1 == "Water", "Water", "Smallpelagic"))))))

df_sample<-df_new %>% 
  left_join(nrow_xyz, by = c("Category" = "Var1")) %>% 
  group_by(Category, stressor) %>% 
  mutate(samples = rlnorm(Freq, meanlog = meanlog, sdlog = sdlog) %>% list) %>% 
  unnest(samples) %>% 
  mutate(Cat = ifelse(Category == "Bovine Meat (Beef Herd)", "Beef",
                      ifelse(Category == "Fish (farmed)", "Salmon aquaculture",
                             ifelse(Category == "Maize (Meal)", "Corn",
                                    ifelse(Category == "Smallpelagic", "Small pelagic fishery", NA))))) %>% 
  as.data.frame()
```



## Check sampled numbers to see how they compare to real data


```{r}
df_sample %>% 
  ggplot(aes(samples)) + 
  geom_histogram() + 
  facet_grid(Category ~ stressor, scales = "free")
```

# Yield/Production data

Yield needs to be in kg liveweight to match the pressure values

```{r}
# Maize 9.97 tonnes dry weight/ha
# Beef 12.185 kg protein/ha = 70.3 kg liveweight/ha
# Need to figure out salmon and pelagic fishery

yield<-data.frame(Category = c("Maize (Meal)", "Bovine Meat (Beef Herd)", "Fish (farmed)", "Smallpelagic"), High_kg_ha = c(12000, 50, 20000, 8000)) %>% 
  mutate(Low_kg_ha = High_kg_ha/3)%>% 
  left_join(nrow_xyz, by = c("Category" = "Var1"))

yield$SD <- (yield$High_kg_ha-yield$Low_kg_ha)/3.92 # Assume the highs and lows are 95 and 5th quantiles 
yield$ymean <- rowMeans(cbind(yield$Low_kg_ha,yield$High_kg_ha))
# 

```


```{r}
yield

yield<- yield %>% 
  group_by(Category) %>% 
  mutate(yield_samples = rnorm(Freq, mean = ymean, sd = SD) %>% list) %>% 
  unnest(yield_samples) #%>% 

# Assign the minimum value to negative values
idx <- which(yield$yield_samples < 0)

yield$yield_samples[idx] <- yield$Low_kg_ha[idx]

# Assume the mean and that the edges are the 95% confidence intervals 


```

# Plot production

```{r}
yield_plot<-xyz 

yield_plot$prod[yield_plot$layer_Categories == "Beef"]<-yield$yield_samples[yield$Category == "Bovine Meat (Beef Herd)"]
yield_plot$prod[yield_plot$layer_Categories == "Corn"]<-yield$yield_samples[yield$Category == "Maize (Meal)"]
yield_plot$prod[yield_plot$layer_Categories == "Salmon aquaculture"]<-yield$yield_samples[yield$Category == "Fish (farmed)"]
yield_plot$prod[yield_plot$layer_Categories == "Small pelagic fishery"]<-yield$yield_samples[yield$Category == "Smallpelagic"]
```


```{r}
plot_prod <-  yield_plot %>% 
  ggplot() + # Need to make another color scale for the stressors 
  geom_raster(aes(x, y, fill = prod)) +
  theme_nlm(legend_labels = legend_labels, ratio = ratio)+
  geom_tile(data = yield_plot[yield_plot$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
  geom_tile(data = yield_plot[yield_plot$layer_Categories == 'Forest',],aes(x, y), fill = 'grey')


plot_prod
```


```{r}
write.csv(yield, here("outputs", "Theoretical_sampled_yields.csv"))
```


# GHG emissions

All pressure data is in kg of liveweight (corrections made to Poore and Nemecek database from personal communication with Dr. Poore), thus we multiply the yield in each cell by the pressure value to get the pressure value in each plot.
```{r}
# Now make the same figure, but replace the corn values with sampled values from the distribution 
# 

ghg<-xyz 

sub<-df_sample %>% 
      filter(stressor == "GHG_emission") %>% 
      dplyr::select(Cat,samples)

    ghg$samples[ghg$layer_Categories == 'Corn'] <- sub$samples[sub$Cat == "Corn"]
    ghg$samples[ghg$layer_Categories == 'Beef'] <- sub$samples[sub$Cat == "Beef"]
    ghg$samples[ghg$layer_Categories == 'Salmon aquaculture'] <- sub$samples[sub$Cat == "Salmon aquaculture"]
    ghg$samples[ghg$layer_Categories == 'Small pelagic fishery'] <- sub$samples[sub$Cat == "Small pelagic fishery"]
    
    ghg$yield[ghg$layer_Categories == 'Corn'] <- yield$yield_samples[yield$Category == "Maize (Meal)"]
    ghg$yield[ghg$layer_Categories == 'Beef'] <- yield$yield_samples[yield$Category == "Bovine Meat (Beef Herd)"]
    ghg$yield[ghg$layer_Categories == 'Salmon aquaculture'] <- yield$yield_samples[yield$Category == "Fish (farmed)"]
    ghg$yield[ghg$layer_Categories == 'Small pelagic fishery'] <- yield$yield_samples[yield$Category == "Smallpelagic"]
    
    ghg$final_stressor <-ghg$samples * ghg$yield
    ghg$stressor<- "GHG"

```


# Land Use

Cattle, maize and salmon aquaculture will get a value of 1 as they are more or less "stationary" and we assume are industrial scale, completely disturbing the habitat in the area they occupy. Fisheries on the other hand are more transient and thus my have a lower disturbance. For small pelagic fishery we assume a disturbance of 1/3 of that from indsturial, stationary production.

```{r}
lu<-xyz

    lu$samples[lu$layer_Categories == 'Corn'] <- 1
    lu$samples[lu$layer_Categories == 'Beef'] <- 1
    lu$samples[lu$layer_Categories == 'Salmon aquaculture'] <- 1
    lu$samples[lu$layer_Categories == 'Small pelagic fishery'] <- 1/3
```


# Freshwater Withdrawal

```{r}
fw<-xyz

    sub_fw<-df_sample %>% 
      filter(stressor == "Freshwtr_Withdr") %>% 
      dplyr::select(Cat,samples) %>% 
      group_by(Cat)
      
      yield<-yield %>% 
        group_by(Category)
    
    fw$samples[fw$layer_Categories == 'Corn'] <- sub_fw$samples[sub_fw$Cat == "Corn"]
    fw$samples[fw$layer_Categories == 'Beef'] <- sub_fw$samples[sub_fw$Cat == "Beef"]
    fw$samples[fw$layer_Categories == 'Salmon aquaculture'] <- sub_fw$samples[sub_fw$Cat == "Salmon aquaculture"]
    
    fw$yield[fw$layer_Categories == 'Corn'] <- yield$yield_samples[yield$Category == "Maize (Meal)"]
    fw$yield[fw$layer_Categories == 'Beef'] <- yield$yield_samples[yield$Category == "Bovine Meat (Beef Herd)"]
    fw$yield[fw$layer_Categories == 'Salmon aquaculture'] <- yield$yield_samples[yield$Category == "Fish (farmed)"]
    fw$yield[fw$layer_Categories == 'Small pelagic fishery'] <- yield$yield_samples[yield$Category == "Smallpelagic"]
    
    fw$final_stressor <-fw$samples * fw$yield
    
    fw$stressor<-"FW"

    
```



# Cumulative Impact

Collate data for mapping - we need the separated feed/farm values for salmon and beef and the raw values for corn and fish. We can just use the on-farm values.

```{r}
lu<-lu %>% 
  mutate(yield = NA,
         stressor = "Land_Use",
         final_stressor = samples)


map_stress_data<-rbind(ghg, fw, lu)
```


## Rescale stressors
```{r}
# We use the 99th percentile to rescale, but this should be based on sample size

df_rescale <- map_stress_data %>%
  group_by(stressor) %>% 
  mutate(quant = quantile(final_stressor, c(0.9999), na.rm = T),
         rescale = final_stressor/quant,
         rescale = ifelse(rescale >1,1, rescale))
```

```{r}
write.csv(map_stress_data, here("outputs","All_on_farm_stressors.csv"))
write.csv(df_rescale, here("outputs", "All_on_farm_stressors_rescaled.csv"))
```


# Cumulate stressors

# Add rescaled stressors together
```{r}
cum_stress<-df_rescale %>% 
  group_by(x,y, layer_Categories) %>% 
  summarise(cum_stress = sum(rescale, na.rm = T))

```

```{r}
write.csv(cum_stress, here("outputs","Cumulative_stressors.csv"))
```


# On farm vs. off farm emission
The current stressors are only "on- farm stressors" now we calculate the stressors from feed. And just crop/animal pressure accordingly to map cumulative cost.

```{r}

total_prod<-yield %>% 
  group_by(Category) %>% 
  summarise(total_prod = sum(yield_samples, na.rm = T))

prop_feed_actual = c(0.43, 0.22, 0.3, NA, NA) 
prop_feed_ex = c(0.43, 0.7, 0.3, NA, NA)  # orginal prop_feed_ex = c(0.43, 0.7, 0.3, NA, NA), we increase the corn/fish for salmon so the example is "self contained". We assume the remaining feed for cows is pasture from within the landscape.

FCR = c(19,1.1,1.1, NA, NA)

off_farm<-data.frame(Category = c("Bovine Meat (Beef Herd)", "Fish (farmed)", "Fish (farmed)", "Maize (Meal)", "Smallpelagic"), 
                     crop = c("Maize", "Maize", "fish meal", NA, NA), 
                     prop_feed_actual = prop_feed_actual, 
                     prop_feed_ex = prop_feed_ex, 
                     FCR = FCR, 
                     total_prod_kg = c(total_prod$total_prod[[1]], total_prod$total_prod[[2]], total_prod$total_prod[[2]],total_prod$total_prod[[3]], 	total_prod$total_prod[[4]])) %>% 
  mutate(feed_needed_kg = total_prod_kg * FCR,
         crop_needed_kg = feed_needed_kg * prop_feed_ex,
         perc_crop_needed = ifelse(crop == "Maize", crop_needed_kg/total_prod$total_prod[[3]],
                                   ifelse(crop == "fish meal", crop_needed_kg/total_prod$total_prod[[4]], NA)))
# We assume fish oil can be obtained from the same fish used for the meal
```



## GHG off-farm beef and salmon

Calculate values for beef on and off farm pressures (i.e. pressure for beef and pressure from feed)

```{r}

corn_ghg<-ghg %>% 
  filter(layer_Categories == "Corn")

total_corn_ghg<-sum(corn_ghg$final_stressor)

corn_ghg_beef<-total_corn_ghg * off_farm$perc_crop_needed[[1]]


beef_ghg<-ghg %>% 
  filter(layer_Categories == "Beef")

farm_beef_ghg<-sum(beef_ghg$final_stressor)

beef_total_ghg<-farm_beef_ghg + corn_ghg_beef 

perc_beef_ghg_on_farm<-farm_beef_ghg/beef_total_ghg
perc_beef_ghg_increase<-beef_total_ghg/farm_beef_ghg
perc_beef_ghg_feed<-corn_ghg_beef/beef_total_ghg
perc_beef_ghg_feed_farm<-corn_ghg_beef/farm_beef_ghg
```

Calculate farmed fish on vs. off farm pressure

```{r}

#Fish feed

fish_ghg<-ghg %>% 
  filter(layer_Categories == "Small pelagic fishery")

total_fish_ghg<-sum(fish_ghg$final_stressor)

fish_ghg_salmon<-total_fish_ghg * off_farm$perc_crop_needed[[3]]

salmon_ghg<-ghg %>% 
  filter(layer_Categories == "Salmon aquaculture")

# Corn
corn_ghg_salmon<-total_corn_ghg * off_farm$perc_crop_needed[[2]]

farm_salmon_ghg<-sum(salmon_ghg$final_stressor)

salmon_total_ghg<-farm_salmon_ghg + corn_ghg_salmon + fish_ghg_salmon

perc_salmon_ghg_on_farm<-farm_salmon_ghg/salmon_total_ghg
perc_salmon_ghg_increase<-salmon_total_ghg/farm_salmon_ghg
perc_salmon_ghg_feed_corn<-corn_ghg_salmon/salmon_total_ghg
perc_salmon_ghg_feed_fish<-fish_ghg_salmon/salmon_total_ghg
perc_salmon_ghg_feed_farm<-(corn_ghg_salmon + fish_ghg_salmon)/farm_salmon_ghg

```


```{r}
ghg_on_off<- ghg %>% 
  rename(farm_stress = final_stressor) %>% 
  mutate(agg_stress = ifelse(layer_Categories == "Beef", farm_stress * perc_beef_ghg_increase,
                      ifelse(layer_Categories == "Salmon aquaculture", farm_stress * perc_salmon_ghg_increase,
                      ifelse(layer_Categories == "Corn", farm_stress*(1-(off_farm$perc_crop_needed[[1]]+off_farm$perc_crop_needed[[2]])), 
                      ifelse(layer_Categories == "Small pelagic fishery", farm_stress*(1-off_farm$perc_crop_needed[[3]]),farm_stress)))),
         beef_disagg_stress = ifelse(layer_Categories == "Beef", farm_stress ,
                      ifelse(layer_Categories == "Corn", farm_stress - (farm_stress*(1-(off_farm$perc_crop_needed[[1]]))),NA)),
         salmon_disagg_stress = ifelse(layer_Categories == "Salmon aquaculture", farm_stress,
                      ifelse(layer_Categories == "Corn", farm_stress - (farm_stress*(1-(off_farm$perc_crop_needed[[2]]))), 
                      ifelse(layer_Categories == "Small pelagic fishery", farm_stress - (farm_stress*(1-off_farm$perc_crop_needed[[3]])),farm_stress))))

round(sum(ghg_on_off$farm_stress, na.rm = T),0) == round(sum(ghg_on_off$agg_stress,na.rm = T),0)


```

```{r}
write.csv(ghg_on_off, here("outputs",'Beef_salmon_GHG_emissions_footprint.csv'))

```


# Land use on/off farm


```{r}
corn_lu<-lu %>% 
  filter(layer_Categories == "Corn")

total_corn_lu<-sum(corn_lu$samples)

corn_lu_beef<-total_corn_lu * off_farm$perc_crop_needed[[1]]


beef_lu<-lu %>% 
  filter(layer_Categories == "Beef")

farm_beef_lu<-sum(beef_lu$samples)

beef_total_lu<-farm_beef_lu + corn_lu_beef

perc_beef_lu_on_farm<-farm_beef_lu/beef_total_lu
perc_beef_lu_increase<-beef_total_lu/farm_beef_lu
perc_beef_lu_feed_corn<-corn_lu_beef/beef_total_lu
perc_beef_lu_feed_farm<-corn_lu_beef/farm_beef_lu


```


```{r}

corn_lu_salmon<-total_corn_lu * off_farm$perc_crop_needed[[2]]

fish_lu<-lu %>% 
  filter(layer_Categories == "Small pelagic fishery")

total_fish_lu<-sum(fish_lu$samples)

fish_lu_salmon<-total_fish_lu * off_farm$perc_crop_needed[[3]]


salmon_lu<-lu %>% 
  filter(layer_Categories == "Salmon aquaculture")

# Corn
farm_salmon_lu<-sum(salmon_lu$samples)
salmon_total_lu<-farm_salmon_lu + fish_lu_salmon + corn_lu_salmon

perc_salmon_lu_on_farm<-farm_salmon_lu/salmon_total_lu
perc_salmon_lu_increase<-salmon_total_lu/farm_salmon_lu
perc_salmon_lu_feed_corn<-corn_lu_salmon/salmon_total_lu
perc_salmon_lu_feed_fish<-fish_lu_salmon/salmon_total_lu
perc_salmon_lu_feed_farm<-(corn_lu_salmon+ fish_lu_salmon)/farm_salmon_lu

```



```{r}
lu_on_off<- lu %>% 
  rename(farm_stress = final_stressor) %>% 
  mutate(agg_stress = ifelse(layer_Categories == "Beef", farm_stress * perc_beef_lu_increase,
                      ifelse(layer_Categories == "Salmon aquaculture", farm_stress * perc_salmon_lu_increase,
                      ifelse(layer_Categories == "Corn", farm_stress*(1-(off_farm$perc_crop_needed[[1]]+off_farm$perc_crop_needed[[2]])), 
                      ifelse(layer_Categories == "Small pelagic fishery", farm_stress*(1-off_farm$perc_crop_needed[[3]]),farm_stress)))))

round(sum(lu_on_off$farm_stress, na.rm = T),0) == round(sum(lu_on_off$agg_stress,na.rm = T),0)
```


# Freshwater on/off farm

```{r}

corn_fw<-fw %>% 
  filter(layer_Categories == "Corn")

total_corn_fw <- sum(corn_fw$final_stressor)

corn_fw_beef<-total_corn_fw * off_farm$perc_crop_needed[[1]]

beef_fw<-fw %>% 
  filter(layer_Categories == "Beef")

farm_beef_fw<-sum(beef_fw$final_stressor)

total_beef_fw<-farm_beef_fw + corn_fw_beef

perc_beef_fw_on_farm<-farm_beef_fw/total_beef_fw
perc_beef_fw_increase<-total_beef_fw/farm_beef_fw
perc_beef_fw_feed<-corn_fw_beef/total_beef_fw
perc_beef_fw_feed_farm<-corn_fw_beef/farm_beef_fw #Multiply the beef farm cell values by this to get the feed values, then sum to get the total pressure

```


```{r}

corn_fw_salmon<-total_corn_fw * off_farm$perc_crop_needed[[2]]

fish_fw<-fw %>% 
  filter(layer_Categories == "Small pelagic fishery")

total_fish_fw<-sum(fish_fw$final_stressor,na.rm = T)

fish_fw_salmon<-total_fish_fw * off_farm$perc_crop_needed[[3]]


salmon_fw<-fw %>% 
  filter(layer_Categories == "Salmon aquaculture")

# Corn
farm_salmon_fw<-sum(salmon_fw$final_stressor)

total_salmon_fw<-farm_salmon_fw + (corn_fw_salmon + fish_fw_salmon)

perc_salmon_fw_on_farm<-farm_salmon_fw/total_salmon_fw
perc_salmon_fw_increase<-total_salmon_fw/farm_salmon_fw
perc_salmon_fw_feed_corn<-corn_fw_salmon/total_salmon_fw
perc_salmon_fw_feed_fish<-fish_fw_salmon/total_salmon_fw
perc_salmon_fw_feed_farm<-(fish_fw_salmon + corn_fw_salmon)/farm_salmon_fw

```

```{r}
fw_on_off<- fw %>% 
  rename(farm_stress = final_stressor) %>% 
  mutate(agg_stress = ifelse(layer_Categories == "Beef", farm_stress * perc_beef_fw_increase,
                      ifelse(layer_Categories == "Salmon aquaculture", farm_stress * perc_salmon_fw_increase,
                      ifelse(layer_Categories == "Corn", farm_stress*(1-(off_farm$perc_crop_needed[[1]]+off_farm$perc_crop_needed[[2]])), 
                      ifelse(layer_Categories == "Small pelagic fishery", farm_stress*(1-off_farm$perc_crop_needed[[3]]),farm_stress)))))

round(sum(fw_on_off$farm_stress, na.rm = T),0) == round(sum(fw_on_off$agg_stress,na.rm = T),0)
```

# Total on-farm and feed stressor for cumulative cost mapping

```{r}
cost_dat<-ghg_on_off %>% 
  dplyr::select(-beef_disagg_stress, -salmon_disagg_stress) %>% 
  rbind(., lu_on_off, fw_on_off) %>% 
  left_join(.,  yield_plot, by = c("layer_Categories", "x", "y")) %>% 
            mutate(cost= agg_stress/prod)

cost_dat_rescale <- cost_dat %>%
  group_by(stressor) %>% 
  mutate(quant = quantile(cost, c(0.9999), na.rm = T),
         rescale = cost/quant,
         rescale = ifelse(rescale >1,1, rescale))
```


# Calculate stressor cost

```{r}
cum_cost<-cost_dat_rescale %>% 
  group_by(x,y, layer_Categories) %>% 
  summarise(cum_cost = sum(rescale, na.rm = T))

```


```{r}
write.csv(cost_dat, here("outputs", "Aggregated_pressures.csv"))
write.csv(cum_cost, here("outputs", "Cumulative_cost.csv"))

```