---
title: "Theoretical example plots"
author: "Caitie"
date: "10/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#devtools::install_github("johannesbjork/LaCroixColoR", force=TRUE) #newest lacroix

library(tidyr)
library(ggplot2)
library(ggsci)
library(NLMR)
library(here)
library(landscapetools)
library(dplyr)
library(reshape2)
library(fitdistrplus)
library(logspline)
library(MASS)
library(raster)
library(here)
library(purrr)
library(ggplot2)
library(ggpubr)
library(broom)
library(LaCroixColoR)
library(gridExtra)
library(tidyr)
library(data.table)
library(viridis)
library(png) #reading in the png images
library(grid) #for rasterising png

source(here("scripts",'theme_nlm_nis.R'))

options(scipen=10000)

```

## Figure 1

Figure 1 is a flow diagram that was heavily modified in powerpoint and thus not include here.

## Figure 2 

Figure 2 plots the individual pressures for each food production type. These plots were saved with a transparent background and overlaid in powerpoint to achieve the final Figure 2 in the manuscript.

## Plot a simulated map of corn data

```{r}
set.seed(1234) # For reproducibility

fbm2 <- NLMR::nlm_fbm(100, 100, fract_dim = 1.1, resolution = 200) # Fractal dimension changes the landscape

plot(fbm2)

x <- util_classify(fbm2, weighting = c(0.1, 0.1, 0.3, 0.3, 0.03, 0.1), level_names = c("Maize","Beef", "Forest", "Water","Salmon aquaculture", "Small pelagic fishery"))
plot(x)

ratio <- nrow(x) / ncol(x)
legend_labels <-  x@data@attributes[[1]][, 2]

xyz  <- raster::as.data.frame(x, xy = TRUE)

landscape <-  ggplot(xyz) +
  geom_tile(aes(x, y, fill = factor(xyz[, 3])))+
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme(panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())+
  theme_nlm_nis(legend_labels = legend_labels, ratio = ratio)+
  scale_fill_manual(values = c('#d65e00', "#009E73", '#F0E442',"#CC79A7",'lightblue', "dodgerblue4"))+ 
  
  guides(fill=guide_legend(title="Landscape"))


landscape   
```



```{r}
png(here("figures","Theoretical_landscape.png"), width = 10, height = 8, units = "in", res = 300)

landscape

dev.off()
```


```{r}
nrow_xyz<-table(xyz$layer_Categories) %>% 
  as.data.frame(row.names = NULL) %>% 
  mutate(Var1 = ifelse(Var1 == "Beef", "Bovine Meat (Beef Herd)", 
                       ifelse(Var1 == "Salmon aquaculture", "Fish (farmed)", 
                              ifelse(Var1 == "Maize","Maize (Meal)",
                                     ifelse(Var1 == "Forest", "Forest", 
                                            ifelse( Var1 == "Water", "Water", "Smallpelagic"))))))

```

# Plot function

```{r}
total_stress_plots<-function(dat, title){
  
    q<-as.numeric(quantile(dat$final_stressor/1000, na.rm = T)) 
    
    dat %>% 
    ggplot() + # Need to make another color scale for the stressors 
    geom_raster(aes(x, y, fill = final_stressor/1000)) +
    #scale_colour_continuous(type = "viridis", direction = -1) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = title)+
    #scale_fill_gradient
    scale_fill_viridis(option = "cividis",direction = -1) +
    geom_tile(data = dat[dat$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = dat[dat$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') 
}
```

# All pressures

```{r}
all_stress<-read.csv(here("outputs","All_on_farm_stressors.csv")) %>% 
      dplyr::select(x,y, layer_Categories, final_stressor, stressor)
```


# Figure 2

The following plots were combined manually in powerpoint to produce Figure 2 in the manuscript


```{r}

# Corn

corn_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Corn") %>% 
    ggplot() +
    geom_tile(aes(x, y, fill = final_stressor/1000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions",
              strip.background = "transparent")+
    scale_fill_gradient(low = "#F0E442",
                      high = "tan4", limits = c(0,250)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 


corn_ghg_plot
```

```{r}
png(here("figures","Corn_GHG_emissions.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

corn_ghg_plot

dev.off()
```

```{r}
log_corn_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Corn") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions",
              strip.background = "transparent")+
    scale_fill_gradient(low = "#F0E442",
                      high = "#8a6c0b", limits = c(0,5.5)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 


log_corn_ghg_plot
```

```{r}
png(here("figures","Corn_GHG_emissions_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_corn_ghg_plot

dev.off()
```


```{r}
# Beef

beef_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Beef") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor/1000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Beef GHG emissions")+
    scale_fill_gradient(low = "#D55E00",
                      high = "gray7",
                      limits = c(0,250)) + 
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 


beef_ghg_plot
```

```{r}
png(here("figures","Beef_GHG_emissions.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

beef_ghg_plot

dev.off()
```


```{r}
log_beef_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Beef") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Beef GHG emissions")+
    scale_fill_gradient(low = "#ffdabe",
                      high = "#d65e00",
                      limits = c(0,5.5)) + 
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 


log_beef_ghg_plot
```

```{r}
png(here("figures","Beef_GHG_emissions_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_beef_ghg_plot

dev.off()
```


```{r}
# Salmon

salmon_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Salmon aquaculture") %>% 
    ggplot() +  
    geom_tile(aes(x, y, fill = final_stressor/1000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions")+
    scale_fill_gradient(low = "#CC79A7",
                      high = "darkorchid4",
                      limits = c(0,250)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 

salmon_ghg_plot
```


```{r}
png(here("figures","Salmon_GHG_emissions.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

salmon_ghg_plot

dev.off()
```


```{r}
# Salmon

log_salmon_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Salmon aquaculture") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions")+
    scale_fill_gradient(low = "#CC79A7",
                      high = "darkorchid4",
                      limits = c(0,5.5)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'transparent') 

log_salmon_ghg_plot
```


```{r}
png(here("figures","Salmon_GHG_emissions_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_salmon_ghg_plot

dev.off()
```


```{r}
# Fishery

fishery_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Small pelagic fishery") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor/1000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions")+
    scale_fill_gradient(low = "lightblue",
                      high = "midnightblue",
                      limits = c(0,250)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') 


fishery_ghg_plot
```

```{r}
png(here("figures","Fishery_GHG_emissions.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

fishery_ghg_plot

dev.off()
```

```{r}
log_fishery_ghg_plot <-  ghg %>% 
    filter(layer_Categories == "Small pelagic fishery") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "GHG emissions")+
    scale_fill_gradient(low = "lightblue",
                      high = "midnightblue",
                      limits = c(0,5.5)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') 


log_fishery_ghg_plot
```

```{r}
png(here("figures","Fishery_GHG_emissions_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_fishery_ghg_plot

dev.off()
```

# Freshwater


```{r}
  fw<-  all_stress %>%
    filter(stressor == "FW") %>%
    mutate(final_stressor_log = log10(final_stressor+1))

    fw_plot <- total_stress_plots(fw, "FW")+ geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey') 
  

    fw_plot 
```


```{r}

# Corn

corn_fw_plot <-  fw %>% 
    filter(layer_Categories == "Corn") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor/100000000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Corn_FW",
              strip.background = "transparent")+
      scale_fill_gradient(low = "#F0E442",
                      high = "tan4",
                      limits = c(0,54286406)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey') 
    


corn_fw_plot
```

```{r}
png(here("figures","Corn_FW.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

corn_fw_plot

dev.off()
```

```{r}

# Corn

log_corn_fw_plot <-  fw %>% 
    filter(layer_Categories == "Corn") %>% 
    ggplot() +
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Corn_FW",
              strip.background = "transparent")+
      scale_fill_gradient(low = "#F0E442",
                      high = "#8a6c0b",
                      limits = c(0,16.1)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey') 
    


log_corn_fw_plot
```

```{r}
png(here("figures","Corn_FW_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_corn_fw_plot

dev.off()
```


```{r}
# Beef

beef_fw_plot <-  fw %>% 
    filter(layer_Categories == "Beef") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill =final_stressor/100000000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Beef FW")+
   scale_fill_gradient(low = "#D55E00",
                      high = "gray7",
                      limits = c(0,54286406)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey') 


beef_fw_plot
```

```{r}
# Beef

log_beef_fw_plot <-  fw %>% 
    filter(layer_Categories == "Beef") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill =final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "Beef FW")+
   scale_fill_gradient(low = "#ffdabe",
                      high = "#d65e00",
                      limits = c(0, 16.1)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey') 


log_beef_fw_plot
```


```{r}
png(here("figures","Beef_FW_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_beef_fw_plot

dev.off()
```

```{r}
# Salmon

salmon_fw_plot <-  fw %>% 
    filter(layer_Categories == "Salmon aquaculture") %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = final_stressor/100000000)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "FW")+
     scale_fill_gradient(low = "#CC79A7",
                      high = "darkorchid4",
                      limits = c(0,54286406)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey')

  
salmon_fw_plot
```

```{r}
png(here("figures", "Salmon_FW.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

salmon_fw_plot

dev.off()
```

```{r}
# Salmon

log_salmon_fw_plot <-  fw %>% 
    filter(layer_Categories == "Salmon aquaculture") %>% 
    ggplot() +
    geom_tile(aes(x, y, fill = final_stressor_log)) +
    theme_nlm(legend_labels = legend_labels,ratio = ratio, legend_title = "FW")+
     scale_fill_gradient(low = "#CC79A7",
                      high = "darkorchid4",
                      limits = c(0, 16.1)) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Corn',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Beef',],aes(x, y), fill = 'transparent') +
    geom_tile(data = ghg[ghg$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey')

  
log_salmon_fw_plot
```

```{r}
png(here("figures", "Salmon_FW_log.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

log_salmon_fw_plot

dev.off()
```

# Land use all production types


```{r}

lu<-  all_stress %>%
    filter(stressor == "Land_Use")

    lu_plot <-  lu %>% 
    ggplot() + 
    geom_raster(aes(x, y, fill = final_stressor)) +
    scale_colour_continuous(type = "viridis") +
    theme_nlm(legend_labels = legend_labels, ratio = ratio, legend_title = "Area occupancy")+
    geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'grey')
  
    lu_plot
```

```{r}
sub_lu<-  lu %>% 
  mutate(layer_Categories = ifelse(layer_Categories == "Corn", "Maize", as.character(layer_Categories)))
    
lu_cat_plot <-  sub_lu %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = factor(test[, 3]))) + theme_bw()+
  theme_nlm_nis(legend_labels = legend_labels, ratio = ratio)+
  scale_fill_manual(values = c('#d65e00', "grey", '#F0E442',"#CC79A7",'lightblue', "grey"))+ 
  guides(fill=guide_legend(title="Land use")) +
    geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'grey')
  
    lu_cat_plot
```

```{r}
png(here("figures", "Land_use_categories.png"), width = 10, height = 8, units = "in", res = 300, bg = "transparent")

lu_cat_plot

dev.off()
```

# Rescaled

```{r}
df_rescale<-read.csv(here("outputs", "All_on_farm_stressors_rescaled.csv"))
```

```{r}
ghg_rescale<-xyz

sub_ghg_rescale<-df_rescale %>% 
      filter(stressor == "GHG")
    
    ghg_rescale_plot <-  sub_ghg_rescale %>% 
    ggplot() + 
    geom_tile(aes(x, y, fill = rescale)) +
    theme_nlm(legend_labels = legend_labels, ratio = ratio)+
    scale_fill_viridis(option = "cividis",direction = -1) +
    geom_tile(data = ghg[ghg$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = ghg[ghg$layer_Categories == 'Forest',],aes(x, y), fill = 'grey')
  
   ghg_rescale_plot
```


```{r}

sub_lu_rescale<-df_rescale %>% 
      filter(stressor == "Land_Use")
    
    lu_rescale_plot <-  sub_lu_rescale %>% 
    ggplot() + # Need to make another color scale for the stressors 
    geom_tile(aes(x, y, fill = rescale)) +
    theme_nlm(legend_labels = legend_labels, ratio = ratio)+
    scale_fill_viridis(option = "cividis",direction = -1) +
    geom_tile(data = lu[lu$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = lu[lu$layer_Categories == 'Forest',],aes(x, y), fill = 'grey')

  
    lu_rescale_plot
```


```{r}
sub_fw_rescale<-df_rescale %>% 
      filter(stressor == "FW") 
    
    
    fw_rescale_plot <-  sub_fw_rescale %>% 
    ggplot() +
    geom_tile(aes(x, y, fill = rescale)) +
    theme_nlm(legend_labels = legend_labels, ratio = ratio)+
    scale_fill_viridis(option = "cividis",direction = -1) +
    geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'grey')+
    geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'grey') +
    geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'grey')

  
   fw_rescale_plot
```

## Figure 3 plots

# Figure 3A

# Cumulative

```{r}
cum_stress<-read.csv(here("outputs", "Cumulative_stressors.csv"))
```

```{r}
plot_c <-  cum_stress %>% 
  ggplot() + 
  geom_tile(aes(x, y, fill = cum_stress))+
  theme_bw()+
  scale_fill_viridis(option = "B",direction = -1, breaks=c(0, 0.5, 1,1.5,2)) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  geom_tile(data = cum_stress[cum_stress$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = cum_stress[cum_stress$layer_Categories == 'Forest',],aes(x, y), fill = 'white')#+


plot_c


max(cum_stress$cum_stress)
```

```{r}
png(here("figures", "Cumulative_pressure.png"), width = 10, height = 8, units = "in", res = 300)

plot_c

dev.off()
```

# Figure 3B

# Plot pressure per unit production

```{r}
cost_dat<-read.csv(here("outputs", "Cumulative_cost.csv"))

```


```{r}
plot_cost <-  cost_dat %>% 
  ggplot() + 
  geom_raster(aes(x, y, fill = cum_cost)) +
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, breaks=c(0, 0.25, 0.5,0.75,1)) +
  theme(legend.title = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  geom_tile(data = cost_dat[cost_dat$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = cost_dat[cost_dat$layer_Categories == 'Forest',],aes(x, y), fill = 'white')#+


plot_cost
```

```{r}
png(here("figures", "Cumulative_cost.png"), width = 10, height = 8, units = "in", res = 300)

plot_cost

dev.off()

```


#Combined Figure 3 plot
```{r}
ggarrange(plot_c, plot_cost,
          labels= c("a.", "b."),
          nrow=1, ncol=2,
          label.y = 1,
          font.label = list(size=12))+
  ggsave(here("figures", "Cumulative_cost_combined.png"), device = "png", width = 10, dpi=300, height = 4.5, units = "in" )+
  ggsave(here("figures", "Cumulative_cost_combined.pdf"), device = "pdf", width = 10, dpi=300, height = 4.5, units = "in" )

```

# Box 2 plot

# Beef on-off GHG emissions

```{r}
ghg_on_off<-read.csv(here("outputs",'Beef_salmon_GHG_emissions_footprint.csv'))

```


```{r}
cow <- readPNG(here("figures", "cow_small.png"))
cow <- rasterGrob(cow)

salmon <- readPNG(here("figures", "salmon.png"))
salmon <- rasterGrob(salmon)
```


```{r}
beef_agg_stress<-ghg_on_off %>% 
  filter(layer_Categories == "Beef") %>% 
  ggplot() +
  geom_tile(aes(x, y, fill = agg_stress/1000)) +
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,115)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'white') +
  geom_tile(data = xyz[xyz$layer_Categories == 'Corn',],aes(x, y), fill = 'white')+
  annotation_custom(cow, xmin = 17000, xmax = 20000, ymin = 18000, ymax=20000)
  
 

beef_agg_stress
```

```{r}
png(here("figures", "Beef_ghg_combined.png"), width = 10, height = 8, units = "in", res = 300)

beef_agg_stress

dev.off()
```

```{r}
beef_disagg<-ghg_on_off %>% 
  ggplot() +
  geom_tile(aes(x, y, fill = beef_disagg_stress/1000)) +
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,115)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'white')+
  annotation_custom(cow, xmin = 17000, xmax = 20000, ymin = 18000, ymax=20000)#+

beef_disagg
```

```{r}
png(here("figures", "Beef_ghg_separated.png"), width = 10, height = 8, units = "in", res = 300)

beef_disagg

dev.off()
```
# Salmon GHG emissions


```{r}
salmon_agg<-ghg_on_off %>% 
  filter(layer_Categories == "Salmon aquaculture") %>% 
  ggplot() +
  geom_tile(aes(x, y, fill = agg_stress/1000)) +
 theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,115)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Beef',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'white') +
  geom_tile(data = xyz[xyz$layer_Categories == 'Corn',],aes(x, y), fill = 'white')+
  annotation_custom(salmon, xmin = 16000, xmax = 20000, ymin = 00, ymax=2000)#+

salmon_agg


```

```{r}
png(here("figures", "Salmon_ghg_combined.png"), width = 10, height = 8, units = "in", res = 300)

salmon_agg

dev.off()
```

```{r}
salmon_disagg<-ghg_on_off %>% 
  ggplot() +
  geom_raster(aes(x, y, fill = salmon_disagg_stress/1000)) +
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,115)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill="transparent"))+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Beef',],aes(x, y), fill = 'white')+
  annotation_custom(salmon, xmin = 16000, xmax = 20000, ymin = 00, ymax=2000)

salmon_disagg

max(ghg_on_off$salmon_disagg_stress[!is.na(ghg_on_off$agg_stress)])
```

```{r}
png(here("figures", "Salmon_ghg_separated.png"), width = 10, height = 8, units = "in", res = 300)

salmon_disagg

dev.off()
```


# Yield/Production data

Yield needs to be in kg liveweight to match the stressor values

```{r}
# Maize 9.97 tonnes dry weight/ha
# Beef 12.185 kg protein/ha = 70.3 kg liveweight/ha
# Need to figure out salmon and pelagic fishery

yield<-data.frame(Category = c("Maize (Meal)", "Bovine Meat (Beef Herd)", "Fish (farmed)", "Smallpelagic"), High_kg_ha = c(12000, 50, 20000, 8000)) %>% 
  mutate(Low_kg_ha = High_kg_ha/3)%>% 
  left_join(nrow_xyz, by = c("Category" = "Var1"))

yield$SD <- (yield$High_kg_ha-yield$Low_kg_ha)/3.92 # Assume the highs and lows are 95 and 5th quantiles 
yield$ymean <- rowMeans(cbind(yield$Low_kg_ha,yield$High_kg_ha))


```


```{r}
yield

yield<- yield %>% 
  group_by(Category) %>% 
  mutate(yield_samples = rnorm(Freq, mean = ymean, sd = SD) %>% list) %>% 
  unnest(yield_samples) #%>% 

# Assign the minimum value to negative values
idx <- which(yield$yield_samples < 0)

yield$yield_samples[idx] <- yield$Low_kg_ha[idx]

# Assume the mean and that the edges are the 95% confidence intervals 


```

```{r}
yield_plot<-xyz 

yield_plot$prod[yield_plot$layer_Categories == "Beef"]<-yield$yield_samples[yield$Category == "Bovine Meat (Beef Herd)"]
yield_plot$prod[yield_plot$layer_Categories == "Maize"]<-yield$yield_samples[yield$Category == "Maize (Meal)"]
yield_plot$prod[yield_plot$layer_Categories == "Salmon aquaculture"]<-yield$yield_samples[yield$Category == "Fish (farmed)"]
yield_plot$prod[yield_plot$layer_Categories == "Small pelagic fishery"]<-yield$yield_samples[yield$Category == "Smallpelagic"]
```


```{r}
yield_fig <-  ggplot(yield_plot) +
  geom_tile(aes(x, y, fill = prod))+
  theme_bw()+
  scale_fill_viridis(option = "B",direction = -1) +
   theme(legend.title = element_blank(),
         panel.grid = element_blank(),
         axis.ticks = element_blank(),
         axis.text = element_blank(),
         axis.title = element_blank())+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  theme(panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank())+
  theme_nlm_nis(legend_labels = legend_labels, ratio = ratio)+
  labs(fill = "")

yield_fig

```


```{r}
png(here("figures","Landscape_yield.png"), width = 10, height = 8, units = "in", res = 300)

yield_fig

dev.off()
```


# Beef_agg_cost

```{r}
ghg_on_off_yield<-left_join(ghg_on_off, yield_plot, by = c("x", "y", "layer_Categories")) %>%
  mutate(agg_cost = agg_stress/yield)
```


```{r}
beef_agg_cost<-ghg_on_off_yield %>% 
  filter(layer_Categories == "Beef") %>% 
  ggplot() +
  geom_tile(aes(x, y, fill = agg_cost)) +
  theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,450)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Salmon aquaculture',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'white') +
  geom_tile(data = xyz[xyz$layer_Categories == 'Corn',],aes(x, y), fill = 'white')+
  annotation_custom(cow, xmin = 17000, xmax = 20000, ymin = 18000, ymax=20000)
  
 

beef_agg_cost
```
# Samlon_agg_cost

```{r}

salmon_agg_cost<-ghg_on_off_yield %>% 
  filter(layer_Categories == "Salmon aquaculture") %>% 
  ggplot() +
  geom_tile(aes(x, y, fill = agg_cost)) +
 theme_bw()+
  coord_equal()+
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_viridis(option = "B",direction = -1, limits = c(0,450)) +
  theme(panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())+
  labs(fill= "")+
  geom_tile(data = xyz[xyz$layer_Categories == 'Water',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Forest',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Beef',],aes(x, y), fill = 'white')+
  geom_tile(data = xyz[xyz$layer_Categories == 'Small pelagic fishery',],aes(x, y), fill = 'white') +
  geom_tile(data = xyz[xyz$layer_Categories == 'Corn',],aes(x, y), fill = 'white')+
  annotation_custom(salmon, xmin = 16000, xmax = 20000, ymin = 00, ymax=2000)#+

salmon_agg_cost

```

#combined box 2 plot with costs
```{r}
ggarrange(beef_disagg, beef_agg_stress, beef_agg_cost, salmon_disagg, salmon_agg, salmon_agg_cost,

          labels = c("a.", "b.", "c.", "d.", "e.", "f."),
          font.label = list(size=12),
          label.y = 1.01,
          nrow = 3, ncol=3,
          align = "hv")
  ggsave(here("figures", "Box_2_figures_combined.png"), width = 14, height = 10, units = "in", dpi=300)
 

```



